Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-18 paper.Rmd
minor edits analysis-script and reprodicing figures

| Conference or event          | Period                  | Online, in person or hybrid | Number of participants | Number of registrations |
|---------------|---------------|---------------|---------------|---------------|
| CAA Amsterdam                | April 2023              | In person                   | 36                     | 53                      |
| EAA Belfast                  | August 2023             | In person                   | 21                     | No registration         |
| CAA-DE/NL-Fl Online workshop | October 2023            | Online                      | 40                     | 76                      |
| Reuvensdagen                 | November 2023           | In person                   | 13                     | No registration         |
| CAA-UK                       | November 2023           | Hybrid                      | 53                     |                         |
| Leiden (course)              | December 2023           | In person                   | 11                     | No registration         |
| Aarhus                       | January/February 2024   | Online                      | 176                    | \>500                   |
| Saxion                       | March 2023-January 2024 | In person                   | 18                     | No registration         |
| **Total**                    |                         |                             | **368**                | **\>628**               |

@@

Funding acknowledgements (need for the part of the APC that I will pay): The Carlsberg Foundation\'s *Young Researcher Fellowship* (CF21-0382).

>>>>

| Conference or event          | Period                  | Online, in person or hybrid | Number of participants | Number of registrations |
|------------------------------|-------------------------|-----------------------------|------------------------|-------------------------|
| CAA Amsterdam                | April 2023              | In person                   | 36                     | 53                      |
| EAA Belfast                  | August 2023             | In person                   | 21                     | No registration         |
| CAA-DE/NL-Fl Online workshop | October 2023            | Online                      | 40                     | 76                      |
| Reuvensdagen                 | November 2023           | In person                   | 13                     | No registration         |
| CAA-UK                       | November 2023           | Hybrid                      | 53                     |                         |
| Leiden (course)              | December 2023           | In person                   | 11                     | No registration         |
| Aarhus                       | January/February 2024   | Online                      | 176                    | \>500                   |
| Saxion                       | March 2023-January 2024 | In person                   | 18                     | No registration         |
| **Total**                    |                         |                             | **368**                | **\>628**               |

@@

Funding acknowledgements (need for the part of the APC that I will pay): The Carlsberg Foundation's *Young Researcher Fellowship* (CF21-0382).
